\documentclass[journal]{IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)


% *** MISC UTILITY PACKAGES ***
\usepackage{url} % Insert URL addresses within the document
\usepackage[colorlinks=false]{hyperref} % Makes internal and external references to clickable links within the PDF document

% *** GRAPHICS RELATED PACKAGES ***
\usepackage[pdftex]{graphicx} % Basic commands to include graphics

% *** MATH PACKAGES ***
\usepackage{amsmath} % Basic commands to depict math equations
\usepackage{bm} % bold font math symbols

% *** CORRECT REPRESENTATION OF SI UNITS ***
\usepackage{siunitx} 

% *** ALIGNMENT PACKAGES ***
\usepackage{array} % nicer lookig tables and 

% *** TABLE PACKAGES ***
\usepackage{booktabs} % nicer tables
\usepackage{multirow} % multi-row cells in tables



\begin{document}

% Check for correct title
\title{\LARGE{Pintos Project I: Threads}}

% Insert your name and student ID here
\author{First Name 1 Last Name 1, Student ID 1 \\\and 
        First Name 2 Last Name 2, Student ID 2 \\\and 
        First Name 3 Last Name 3, Student ID 3} 


%%%% Do not change this %%%%
\markboth{CS2S01 Operating Systems 2021}{CS2S01 Operating Systems 2021}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preliminaries}
%%%% Some instruction words (delete this section for your submission) %%%%
If you have any preliminary comments on your submission, notes for the TAs, or extra credit, please give them here.

Please cite any offline or online sources you consulted while preparing your submission, other than the Pintos documentation, course text, lecture notes, and course staff.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Alarm Clock}
\subsection{Data Structures}
%%%% Some instruction words (delete this section for your submission) %%%%
A1: Copy here the declaration of each new or changed 'struct' or 'struct' member, global or static variable, 'typedef', or enumeration.  Identify the purpose of each in 25 words or less.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Algorithms}
%%%% Some instruction words (delete this section for your submission) %%%%
A2: Briefly describe what happens in a call to timer\_sleep(), including the effects of the timer interrupt handler.

A3: What steps are taken to minimize the amount of time spent in the timer interrupt handler?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synchronization}
%%%% Some instruction words (delete this section for your submission) %%%%
A4: How are race conditions avoided when multiple threads call timer\_sleep() simultaneously?

A5: How are race conditions avoided when a timer interrupt occurs during a call to timer\_sleep()?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rationale}
%%%% Some instruction words (delete this section for your submission) %%%%
A6: Why did you choose this design?  In what ways is it superior to another design you considered?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Priority Scheduling}

\subsection{Data Structures}
%%%% Some instruction words (delete this section for your submission) %%%%
B1: Copy here the declaration of each new or changed 'struct' or'struct' member, global or static variable, 'typedef', or enumeration.  Identify the purpose of each in 25 words or less.

B2: Explain the data structure used to track priority donation. Use an image to diagram a nested donation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Algorithms}
%%%% Some instruction words (delete this section for your submission) %%%%
B3: How do you ensure that the highest priority thread waiting for a lock, semaphore, or condition variable wakes up first?

B4: Describe the sequence of events when a call to lock\_acquire() causes a priority donation.  How is nested donation handled?

B5: Describe the sequence of events when lock\_release() is called on a lock that a higher-priority thread is waiting for.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synchronization}
%%%% Some instruction words (delete this section for your submission) %%%%
B6: Describe a potential race in thread\_set\_priority() and explain  how your implementation avoids it.  Can you use a lock to avoid this race?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rationale}
%%%% Some instruction words (delete this section for your submission) %%%%
B7: Why did you choose this design?  In what ways is it superior to another design you considered?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survey Questions}
%%%% Some instruction words (delete this section for your submission) %%%%
Answering these questions is optional, but it will help us improve the
course in future quarters.  Feel free to tell us anything you
want--these questions are just to spur your thoughts.  You may also
choose to respond anonymously in the course evaluations at the end of
the quarter.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item \textit{In your opinion, was this assignment, or any one of the three problems in it, too easy or too hard?  Did it take too long or too little time?}

\item \textit{Did you find that working on a particular part of the assignment gave you greater insight into some aspect of OS design?}

\item \textit{Is there some particular fact or hint we should give students in future quarters to help them solve the problems?  Conversely, did you find any of our guidance to be misleading?}

\item \textit{Do you have any suggestions for the TAs to more effectively assist students, either for future quarters or the remaining projects?}

\item \textit{Any other comments?}
\end{itemize}

\end{document}


